---
title: "Analysis Netflix"
author: "Emanuel Michele Soda"
date: "11/16/2021"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(forecast)
library(lubridate)
```

# Read data from the tidytuesday project 
The datra are read from the tidytuesday repository using the 
package __tidytuesdayR__. The table is trasformed into a tibble 
for better visualizzation and all the character columns are  
trasformed into factor.
```{r eval=FALSE, include=FALSE}
tuesdata <- tidytuesdayR::tt_load('2021-04-20')
write_csv(x = tuesdata$netflix_titles, file = "tuesdata.csv")
```

Lets set the theme globally 
```{r Set Theme, fig.height=12, fig.width=15}
theme_set(theme_light())
```


```{r Read Data, fig.height=12, fig.width=15}
data <- read_csv(file = "tuesdata.csv") %>%  
  tibble() %>%  
  mutate_if(is_character, factor) 
```

To have a first and quick look of the data we can use the summary function
```{r Summary, fig.height=12, fig.width=15}
data %>%  summary()
```

Lets check if there are __NA__ values. As can be seen the column which has
more na values is director. NB: are plotted oly the column which contains 
at least 1 __NA__.
```{r NA values, fig.height=12, fig.width=15}
data %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.)))) %>%  
  pivot_longer(cols = everything()) %>% 
  filter(value > 0) %>% 
  
  ggplot(., aes(x = value, y = reorder(name, -value), fill = name)) +
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Set3") +
  scale_x_log10() +
  xlab("Number of NA values") + 
  ylab("Column Name") + 
  theme(legend.position = "bottom") 
```

# Data visualization
As can the summary functio shows there are two type of item in the Netflix 
collection __Movie__ and __TV show__, can be interesting to see the number 
of those item released over year. To do this we can compute the cumulative 
sum over time divided in the two groups. As can be seen from the line plot
the number of film release is always bigger than the number of TV Show. 
Moreover, as reported the y axis is in log scale, for this reason the trend 
which is linear in the log scale is actually exponential.
```{r Data manipulation, fig.height=12, fig.width=15}
data %>% 
  group_by(type, release_year) %>% 
  summarize(n=n()) %>%  
  mutate(cum = cumsum(n)) %>% 
  
 ggplot(., aes(x=release_year, y=cum, col=type)) +
  geom_line() +
  scale_y_log10()  +
  scale_color_brewer(palette = "Dark2") + 
  ylab("Log_10 of cumulative number of item released") +
  xlab("Year") +
  theme_light() +
  theme(legend.position = "bottom") +
  ggtitle("Cumlative number of Movie and TV Show released")
```

So, as can be imagine from the first plot the  number of film is much bigger 
than the number of TV show
```{r Trend over time, fig.height=12, fig.width=15}
data %>%  
  group_by(type) %>% 
  count() %>% 
  
  ggplot(., aes(x = type, y = n, fill = type)) +
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Dark2") +
  theme_light() +
  ylab("Number of films") +
  xlab("Type of item") +
  theme(legend.position = "bottom")
```

Could be of interest to see the duration of each item. On this topic as to be 
clarify that the duration is in minutes for what concern the Movie while is 
in season for the TV  Shows. 
```{r Boxplot duratin, fig.height=12, fig.width=15}
data %>% 
  mutate(duration = as.integer(str_split_fixed(duration," ", 2)[, 1])) %>%  
  group_by(type, duration)   %>% 
  summarise(duration, .groups = "drop") %>%  
  
  ggplot(., aes(x = type, y = duration, fill = type)) +
  geom_violin() +
  #geom_boxplot() +
  scale_fill_brewer(palette = "Dark2") +
  theme_light() +
  xlab("Type of item") +
  theme(legend.position = "bottom")   +
  facet_wrap("type", scales = "free") 

```

From the plot can be seen that some TV shows have more than 13 season. Lets
find out which are.
```{r TV shows > 13, fig.height=12, fig.width=15}
data %>% 
mutate(duration = as.integer(str_split_fixed(duration," ", 2)[, 1])) %>%  
  filter(type == "TV Show") %>%  
  filter(duration > 13) %>%  
  summarise(title, duration, cast, country, release_year, description)
```


From the plot can be seen that some Movies are longer than 250 minutes Lets
find out which are.
```{r Movie > 250, fig.height=12, fig.width=15}
data %>% 
mutate(duration = as.integer(str_split_fixed(duration," ", 2)[, 1])) %>%  
  filter(type == "Movie") %>%  
  filter(duration > 250) %>%   
  summarise(title, duration, cast, country, release_year, description)
```

Lets plot the top 3 cuntry by Movie and TV Shows.As can be seen from 
the plot the US has the most Movie and TV Show released
```{r Item for state, fig.height=12, fig.width=15}
data %>%  
  group_by(country, type) %>% 
  count() %>% 
  drop_na() %>% 
  group_by(type) %>% 
  slice_max(order_by = n, n = 3)   %>% 

  ggplot(., aes(x = reorder(country, -n), y = n, fill= country)) +
  geom_bar(stat="identity") +
  #scale_y_log10() +
  scale_fill_brewer(palette = "Set2") +
  theme_light() +
  xlab("Country") +
  ylab("Number of item") +
  theme(legend.position = "top") + 
  facet_wrap("type", scales = "free", ncol = 1)
```

Lets see the item on the Netflix catalog in which is present 
__Leonardo DiCaprio__ as part of the cast.

```{r Leonardo DiCaprio, fig.height=12, fig.width=15}
data  %>% 
  filter(str_detect(string = cast, regex('DiCaprio', ignore_case = T))) %>% 
  summarise(title, type, cast) 
```

Lets see the item on the Netflix catalog in which is present 
__Johnny Depp__ as part of the cast.
```{r Johnny Depp, fig.height=12, fig.width=15}
data  %>% 
  filter(str_detect(string = cast, regex('Depp', ignore_case = T))) %>% 
  summarise(title, type, cast) 
```

lets see the top 5 directorfor number of item present in Netflix
```{r director, fig.height=12, fig.width=15}
data %>% 
  group_by(director) %>% 
  count() %>% 
  drop_na() %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  
  ggplot(., aes(x = n, y = reorder(director, -n), fill= director)) +
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Set3") +
  theme_light() +
  xlab("Number of item") +
  ylab("Director") +
  theme(legend.position = "none") +
  ggtitle("Number of item for director")
  
```

Can be interest interesting to see if the duration of the Movies has changed 
over time. As can be seen from the boxplot this is not the case.

```{r Duration Movie over time, fig.height=12, fig.width=15}
data %>% 
  filter(type == "Movie") %>% 
  mutate(duration = as.integer(str_split_fixed(duration," ", 2)[, 1])) %>% 
  ggplot(., aes(x=release_year, y= duration, 
                group= release_year, fill = release_year)) + 
  geom_boxplot(outlier.shape = NA) +
  theme(legend.position = "none") + 
  ggtitle("Duration in minutes of Movies over time")
```
